Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-28 cav2017/cav2017.tex
edits

There are several cases for which the system may fail to find a controller. 
For the naive approach, the completeness threshold may be too large, thus
causing a timeout.  On the other hand, the abstraction-based approach may
require a very precise abstraction, resulting in too many refinements and,
consequently, a timeout.  Yet another source of incompleteness is the
inability of the {\sc synthesize} phase to use a large enough precision for
the plant model in a given problem.

>>>>

There are several cases for which the system may fail to find a controller. 
For the naive approach, the completeness threshold may be too large, thus
causing a timeout.  On the other hand, the abstraction-based approach may
require a very precise abstraction, resulting in too many refinements and,
consequently, timeout.  Yet another source of incompleteness is the
inability of the {\sc synthesize} phase to use a large enough precision for
the plant model.
